Odonate abundance changes in response to the creation of a flood reservoir in a former fen

### 2020-12-03 manuscript/manuscript.Rmd
more reference and discussion changes

The damselflies and dragonflies in this study are listed in Table 1 for reference. The figure below (Fig. 2), is a linear regression model of the maximum abundance of males in a single day from 1959  to 1988. The abundance corresponds to the sum of the ten species in Table 1 and the p-value for the model was 0.000162.

@@

These fens (as a type of wetland) provide multiple ecosystem services, biodiversity, water quality management, flood management, and carbon storage (Zedler & Kercher, 2005).

>>>>

The damselflies and dragonflies in this study are listed in Table 1 for reference. The figure below (Fig. 2), is a linear regression model of the maximum abundance of males in a single day from 1959  to 1988. The abundance corresponds to the sum of the ten species in Table 1 and the p-value for the model was 0.000162. Figure 3 is the ten LM of the corresponding species, with p-values shown in Table 2. Figure 4 is a model of the total number of species per year over the study period. It does not have a fitted line or a p-value for reasons that will be discussed later.

@@

These fens (as a type of wetland) provide multiple ecosystem services, biodiversity, water quality management, flood management, and carbon storage (Zedler & Kercher, 2005). They are also excellent resources for wildlife hobbyists and local residents as nature reserves. Local residents may be particularly important in the preservation and conservation of fens, as they are the humans most immediately affected by ecosystem changes.
